---
title: "Corruption-and-Human-Development-Plot-Project"
author: "Rohit Shrivastava"
date: "2024-08-28"
output:
  beamer_presentation: default
  slidy_presentation: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Overview: "Corruption and Human Development 2011"

The "Corruption and Human Development" visualizes the relationship
between the Corruption Perceptions Index (CPI) and the Human Development
Index (HDI) for various countries in 2011. The CPI scores range from 0
to 10, with 10 indicating the least corruption, while the HDI ranges
from 0 to 10, with higher scores representing better human development
outcomes. Here's the step-by-step breakdown of the process you've
followed to create the R file for plotting the "Corruption and Human
Development Graph: The Economist"

# Steps:

## Step-1:

Import Libraries and Load Dataset Import necessary libraries: ggplot2
for plotting and data.table for data manipulation. Load the dataset
using the fread function from the data.table package, and drop the first
column. Use the head() function to display the first few rows of the
dataset.

library(ggplot2) library(data.table) df \<-
fread("Economist_Assignment_Data.csv", drop = 1) head(df)

## Step-2:

Create Scatter Plot Create a scatter plot object (pl) using ggplot. Set
the aesthetics with x = CPI, y = HDI, and color = Region. Add points
with specific shape and size using geom_point. pl \<- ggplot(df, aes(x =
CPI, y = HDI)) geom_point(aes(color = Region), shape = 'O', size = 3)

## Step-3:

Add Trend Line Add a trend line to the scatter plot using geom_smooth.
Define the group for the trend line, set the method to linear model
('lm'), use a log transformation for x in the formula, disable standard
error shading (se = FALSE), and set the line color to red.

pl2 \<- pl + geom_smooth(aes(group = 1), method = 'lm', formula = y \~
log(x), se = FALSE, color = 'red')

## Step-4:

Add Labels for Specific Countries Create a list of countries
(PointsToLabel) to label on the graph. Add text labels for these
countries using geom_text. Use check_overlap = TRUE to avoid overlapping
labels.

PointsToLabel \<- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
"Afghanistan", "Congo", "Greece", "Argentina", "Brazil", "India",
"Italy", "China", "South Africa", "Spane", "Botswana", "Cape Verde",
"Bhutan", "Rwanda", "France", "United States", "Germany", "Britain",
"Barbados", "Norway", "Japan", "New Zealand", "Singapore")

pl3 \<- pl2 + geom_text(aes(label = Country), color = 'gray20', data =
subset(df, Country %in% PointsToLabel), check_overlap = TRUE)

## Step-5:

Set Scales and Theme Set the x and y axis scales using
scale_x_continuous and scale_y_continuous with appropriate labels,
limits, and breaks. Apply a clean bw theme to the plot.

pl4 \<- pl3 + theme_bw() pl5 \<- pl4 + scale_x_continuous(name =
'Corruption Perceptions Index, 2011 (10 = Least Corrupt)', limits =
c(0.9, 10.5), breaks = 1:10) + scale_y_continuous(name = 'Human
Development Index, 2011 (11 = Best)', limits = c(0.2, 1.0))

## Step-6:

Set the Title Add a title to the plot using ggtitle.

pl6 \<- pl5 + ggtitle('Corruption and Human Development') print(pl6)
This sequence of steps outlines the creation of the scatter plot that
visually represents the relationship between corruption and human
development, with trend lines and specific labels for selected
countries.

# THANK YOU

## R Output

library(ggplot2) library(data.table)

df \<- fread("Economist_Assignment_Data.csv",drop = 1)

head(df)

pl \<- ggplot(df,aes(x=CPI,y=HDI))
geom_point(aes(color=Region),shape='O',size=3)

pl2 \<- pl + geom_smooth(aes(group=1),method = 'lm',formula = y \~
log(x),se = F,color='red')

PointsToLabel \<- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
"Afghanistan", "Congo", "Greece", "Argentina", "Brazil", "India",
"Italy", "China", "South Africa", "Spane", "Botswana", "Cape Verde",
"Bhutan", "Rwanda", "France", "United States", "Germany", "Britain",
"Barbados", "Norway", "Japan", "New Zealand", "Singapore")

pl3 \<- pl2 + geom_text(aes(label=Country),color='gray20',data =
subset(df,Country %in% PointsToLabel),check_overlap = T)

pl4 \<- pl3 + theme_bw()

pl5 \<- pl4 + scale_x_continuous(name = 'Corruption Perceptions
Index,2011 (10 = Least Corrupt)',limits = c(0.9, 10.5),breaks = 1:10) +
scale_y_continuous(name = 'Human Development Index, 2011 (11 =
Best)',limits = c(0.2, 1.0))

pl6 \<- pl5 + ggtitle('Corruption and Human Development')

print(pl6)

## Plot: Corruption and Human Development

```{r pressure}
plot(pl6)
```
